Redshift evolution of the SN stretch distribution

### 2019-12-06 Nicolas.tex
Update

The goal is to find how the stretch depends on the LsSFR, distinguishing old and
young SNe which fractions evolve with the redshift, in order to have an
analytical law for the mean redshift evolution of the stretch. The measured data
on which we based our first model is plotted in figure \ref{fig:mod_first};
based of the shape of the $x_1$ vs LsSFR cloud, we implemented the following
model:
\begin{itemize}
    \item \textbf{young}: a gaussian of mean $\m_1$ and standard deviation
        $\s_1$, namely $\Nc_1 \equiv \Nc \LF{\m_1,\s_1}$;
    \item \textbf{old}: a linear combination between $\Nc_1$ and another
        gaussian $\Nc_2 \equiv \Nc \LF{\m_2,\s_2}$
\end{itemize}
As such, the probability to observe a young SNe Ia labeled "i" with a stretch
$x_1^i$ and error $\d x_1^i$ is
\begin{equation}
    p \LF{x_1^i, \d x_1{}^i|\m_1,\s_1} = \Nc \LF{\m_1, \Sq{\s_1{}^2 + \d
    x_1^i{}^2}}(x_1^i)
\end{equation}
and for an old one:
\begin{align}
    p(x_1^i, \d x_1^i | \m_{1,2}, \s_{1,2}, a) = a & \times \Nc \LF{\m_1,
    \sqrt{\s_1{}^2 + \d x_1^i{}^{2}}} (x_1^i) \ + \\ (1-a) & \times \Nc
    \LF{\m_2, \sqrt{ \s_2{}^2 + \d x_1^i{}^{2}}} (x_1^i), \nonumber 
\end{align}

\noindent where $a$ is the relative amplitude between the two gaussians.
Finally, the normalized stretch distribution at a given $z$ $\D\LF{x_1|z}$ is
the weigthed sum of both young and old stretch distributions given their
relative fraction $\de\z$:
\begin{equation}
    \D\LF{x_1|z} = \de\z\times\Nc_1 +
    \LF{1-\de\z} \times \LF{a\Nc_1 + (1-a)\Nc_2}
\end{equation}

We fitted it on SNf data, giving the results table \ref{tab:val}, with a graphical representation shown figure \ref{fig:snf_model}. For clarity
with the next models, we named it 3G2M2S$\St{SNf}$ for it has a total of 3
gaussians but with only 2 means and 2 standard deviations, and has been fitted
on SNf data only.

@@

We implemented and compared 10 models in total, 4 of which have an
evolution with the redshift from $\de\z$, and 6 don't ($\de\z = f =
\mathrm{cst}$). The ones with and evolution are:
\begin{itemize}
    \item 3G2M2S, the one we described (but fitted on all the data);
    \item 3G2M1S, where this time $\s_1 \equiv \s_2$;
    \item 2G2M2S, model taken from HOWELL 2009 where we added $\de\z$;
    \item 3G3M3S, with three independent gaussians.
\end{itemize}
The ones without a stretch evolution are the same ones but with an "F" implying
we set $\de\z = f = \mathrm{cst}$, and two others:
\begin{itemize}
    \item 1G1M1S, where there is no distinction between old and young SNe;
    \item 1G1M2S, taken from KESLLER 2017 and used in recent cosmological
        analysis SCOLNIC 2018. It's an asymetric model where
\end{itemize}
\begin{align}
 p(x_1^i, \d x_1^i | \m, \s_-, \s_+) = 
    \begin{cases}
        \mathcal{N} \LF{\m, \sqrt{\s_-{}^2 + \d x_1^i{}^{2}}} (x_1^i) & \text{if
        } x_1^i\geq \m\\
        \mathcal{N} \LF{\m, \sqrt{\s_+{}^2 + \d x_1^i{}^{2}}} (x_1^i), &
        \text{else}
    \end{cases}
\end{align}

@@

        Model & $a$ & $f$ & $\m_1$ & $\s_1$ & $\m_2$ &
        $\s_2$ \\\hline

@@

        3G2M1S & $0.47 \pm 0.07$ & none & $0.35 \pm 0.04$ & $0.61 \pm 0.03$ &
        $-1.25 \pm 0.10$ & $\s_1$ \\

        3G2M1SF & \textcolor{red}{$0.2 \pm 0.9$} & $0.7 \pm 0.3$ & $0.36 \pm
        0.04$ & $0.60 \pm 0.03$ & $-1.23 \pm 0.10$ & $\s_1$ \\

@@

    Model & $\m$ & $\s$ \\\hline

@@

    Model & $\m$ & $\s_-$ & $\s_+$ \\\hline

@@

    Model & $a$ & $f$ & $\m_1$ & $\s_1$ & $\m_2$ & $\s_2$ &
    $m_3$ & $\s_3$ \\\hline

>>>>

The goal is to find how the stretch depends on the LsSFR, distinguishing old and
young SNe which fractions evolve with the redshift, in order to have an
analytical law for the mean redshift evolution of the stretch. The measured data
on which we based our first model is plotted in figure \ref{fig:mod_first};
based of the shape of the $x_1$ vs LsSFR cloud, we implemented the following
model:
\begin{itemize}
    \item \textbf{young}: a gaussian of mean $\m_1$ and standard deviation
        $\s_1$, namely $\Nc_1 \equiv \Nc \LF{\m_1,\s_1}$;
    \item \textbf{old}: a linear combination between $\Nc_1$ and another
        gaussian $\Nc_2 \equiv \Nc \LF{\m_2,\s_2}$
\end{itemize}
As such, the probability to observe a young SNe Ia labeled "i" with a stretch
$x_1^i$ and error $\mathrm{d} x_1^i$ is
\begin{equation}
    p \LF{x_1^i, \mathrm{d} x_1{}^i|\mu_1,\sigma_1} = \mathcal{N} \left(\mu_1,
    \sqrt{\sigma_1{}^2 + \mathrm{d} x_1^i{}^2}\right)(x_1^i)
\end{equation}
and for an old one:
\begin{align}
    p(x_1^i, \mathrm{d} x_1^i | \mu_{1,2}, \sigma_{1,2}, a) = a & \times
    \mathcal{N} \left(\mu_1, \sqrt{\sigma_1{}^2 + \mathrm{d} x_1^i{}^{2}}\right) (x_1^i) \ + \\ (1-a) & \times \mathcal{N}
    \left(\mu_2, \sqrt{ \sigma_2{}^2 + \mathrm{d} x_1^i{}^{2}}\right) (x_1^i), \nonumber 
\end{align}

\noindent where $a$ is the relative amplitude between the two gaussians.
Finally, the normalized stretch distribution at a given $z$
$\Delta\left(x_1|z\right)$ is
the weigthed sum of both young and old stretch distributions given their
relative fraction $\delta(z)$:
\begin{equation}
    \Delta\left(x_1|z\right) = \delta(z)\times\mathcal{N}_1 +
    \left(1-\delta(z)\right) \times \left(a\mathcal{N}_1 +
    (1-a)\mathcal{N}_2\right)
\end{equation}

We fitted it on SNf data, giving the results table \ref{tab:val}, with a graphical representation shown figure \ref{fig:snf_model}. For clarity
with the next models, we named it 3G2M2S$_{\text{SNf}}$ for it has a total of 3
gaussians but with only 2 means and 2 standard deviations, and has been fitted
on SNf data only.

@@

We implemented and compared 10 models in total, 4 of which have an
evolution with the redshift from $\delta(z)$, and 6 don't ($\delta(z) = f =
\mathrm{cst}$). The ones with and evolution are:
\begin{itemize}
    \item 3G2M2S, the one we described (but fitted on all the data);
    \item 3G2M1S, where this time $\sigma_1 \equiv \sigma_2$;
    \item 2G2M2S, model taken from HOWELL 2009 where we added $\delta(z)$;
    \item 3G3M3S, with three independent gaussians.
\end{itemize}
The ones without a stretch evolution are the same ones but with an "F" implying
we set $\delta(z) = f = \mathrm{cst}$, and two others:
\begin{itemize}
    \item 1G1M1S, where there is no distinction between old and young SNe;
    \item 1G1M2S, taken from KESLLER 2017 and used in recent cosmological
        analysis SCOLNIC 2018. It's an asymetric model where
\end{itemize}
\begin{align}
 p(x_1^i, \mathrm{d} x_1^i | \mu, \sigma_-, \sigma_+) = 
    \begin{cases}
        \mathcal{N} \left(\mu, \sqrt{\sigma_-{}^2 + \mathrm{d} x_1^i{}^{2}}\right) (x_1^i) & \text{if
        } x_1^i\geq \mu\\
        \mathcal{N} \left(\mu, \sqrt{\sigma_+{}^2 + \mathrm{d} x_1^i{}^{2}}\right) (x_1^i), &
        \text{else}
    \end{cases}
\end{align}

@@

        Model & $a$ & $f$ & $\mu_1$ & $\sigma_1$ & $\mu_2$ &
        $\sigma_2$ \\\hline

@@

        3G2M1S & $0.47 \pm 0.07$ & none & $0.35 \pm 0.04$ & $0.61 \pm 0.03$ &
        $-1.25 \pm 0.10$ & $\sigma_1$ \\

        3G2M1SF & \textcolor{red}{$0.2 \pm 0.9$} & $0.7 \pm 0.3$ & $0.36 \pm
        0.04$ & $0.60 \pm 0.03$ & $-1.23 \pm 0.10$ & $\sigma_1$ \\

@@

    Model & $\mu$ & $\sigma$ \\\hline

@@

    Model & $\mu$ & $\sigma_-$ & $\sigma_+$ \\\hline

@@

    Model & $a$ & $f$ & $\mu_1$ & $\sigma_1$ & $\mu_2$ & $\sigma_2$ &
    $\mu_3$ & $\sigma_3$ \\\hline
